### 2019-01-25 journal/experiments.tex
in

Alternatively, a radical way to produce ``hot'' mutants at low cost (the only significant cost being that of executing the test suite to throw out mutants killed by some passing test) is to produce mutants at the \emph{object code} level, which does not require recompiling a system.  This is how SQLite applies mutation testing:  \url{https://www.sqlite.org/testing.html#mutation_testing}.  Object level mutants are obviously not useful (or at least, certainly not \emph{as} useful) for fault localization as source-level mutants, but they mutating branches alone probably captures many compiler repairs that are useful in fuzzer taming.

@@

Mutation cost reduction techniques classified as \emph{do fewer} on the other hand involve a loss of signal, not just more efficient production of the same signal.  Figures \ref{samplejs} and \ref{samplegcc} show, respectively, the results of random sampling of mutants for SpiderMonkey and GCC, by comparing the APFD obtained on a set of 30 random samples of the chosen percentage of mutants with the APFD for the full mutant set.  Because some mutants are actually misleading with respect to distinguishing faults, sometimes sampling can improve results.  Sampling 10\% of mutants directly translates to our approach requiring about 90\% less time (or less computing power if run in parallel).  We assume a ``hot'' mutants approach in that our sampling is of compilable, test-passing mutants.  A larger sample would be required, in proportion to how many mutants compile and pass tests, to achieve the same results in a scenario with only ``cold'' mutants, though the difference is not huge, since most mutants are ruled out by the fact that no passing test covers the mutant, rather than that they cause some passing test to fail.  The more significant difference in a cold-mutant scenario is that each mutant/test evaluation is of course much cheaper without the cost (even amortized over many tests) of compilation, not the total number of mutants considered.

@@

>>>>

Alternatively, a radical way to produce ``hot'' mutants at low cost (the only significant cost being that of executing the test suite to throw out mutants killed by some passing test) is to produce mutants at the \emph{object code} level, which does not require recompiling a system.  This is how SQLite applies mutation testing:  \url{https://www.sqlite.org/testing.html#mutation_testing}.  Object level mutants are obviously not useful (or at least, certainly not \emph{as} useful) for fault localization as source-level mutants, but mutating branches alone probably captures many compiler repairs that are useful in fuzzer taming.

@@

\subsubsection{Random Sampling}

Mutation cost reduction techniques classified as \emph{do fewer} on the other hand involve a loss of signal, not just more efficient production of the same signal.   One of the most popular and simple approaches to reducing the cost of mutation testing is \emph{random sampling} \cite{budd1980mutation,acree1980mutation,RahulISSRE,MutRand}.
 Figures \ref{samplejs} and \ref{samplegcc} show, respectively, the results of random sampling of mutants for SpiderMonkey and GCC, by comparing the APFD obtained on a set of 30 random samples of the chosen percentage of mutants with the APFD for the full mutant set.  Because some mutants are actually misleading with respect to distinguishing faults, sometimes sampling can improve results.  Sampling 10\% of mutants directly translates to our approach requiring about 90\% less time (or less computing power if run in parallel).  We assume a ``hot'' mutants approach in that our sampling is of compilable, test-passing mutants.  A larger sample would be required, in proportion to how many mutants compile and pass tests, to achieve the same results in a scenario with only ``cold'' mutants, though the difference is not huge, since most mutants are ruled out by the fact that no passing test covers the mutant, rather than that they cause some passing test to fail.  The more significant difference in a cold-mutant scenario is that each mutant/test evaluation is of course much cheaper without the cost (even amortized over many tests) of compilation, not the total number of mutants considered.

@@

\subsubsection{Operator-Based Selection}

A deterministic alternative to random sampling, long used in the mutation testing community, is operator-based selection, where only some mutation operators are applied \cite{wong1995reducing,untch2009onreduced}.  Using \emph{only statement deletion and condition negation mutants}, as in our toy example, on the grounds that we expect most compiler ``repairs'' to simply avoid an optimization, not actually fix a simple defect such as an off-by-one error in a loop, is an intuitively appealing and trivial to implement approach.  The idea is clearly related to the object-level branch-mutation proposed above, conceptually, but operating at the (more understandable to humans, and thus useful in localization) source level.  The resulting cost reduction is significant:  67.8\% of mutants can be ignored for SpiderMonkey, and 73\% for GCC.  More importantly, the APFD actually \emph{improves} with this change.  For SpiderMonkey, the APFD improves by almost 3\%, and for GCC, it improves by 0.86\%.  For SpiderMonkey, the early curve (first ten items) is improved, and for GCC it is very slightly worse.  Most importantly, in both cases, two additional faults are revealed in the first 50 examined tests.
